---
title: "BootStrapping"
format: html
editor: visual
---

```{r}
# Package names
packages <- c(
  # import data
  "readr",
  "readxl",
  "openxlsx",
  
  # syntax
  "plyr",
  "dplyr",
  "tidyverse",
  
  # cleaning 
  "janitor", 
  "broom",
  
  # date 
  "lubridate",
  
  # graphs 
  "ggplot2",
  "ggrepel",
  "ggsignif",
  "gridExtra",
  "ggpubr",
  "plotly",
  "scales",
  "cowplot",
  "magick",
  
  # tables
  "DT",
  
  # knit 
  "knitr",
  
  # spatial data
  "sf", # spatial maipulation
  "tmap", # map making
  "grid", # viewport
  
  # string manipulation 
  "stringr",
  
  # Beta models 
  "betareg")

# Install packages not yet installed
installed_packages <- packages %in% rownames(installed.packages())
if (any(installed_packages == FALSE)) {
  install.packages(packages[!installed_packages])
}

# Packages loading
invisible(lapply(packages, library, character.only = TRUE))

rm(installed_packages, packages)
```

```{r}
# Metadata
load("data/info.Rda")

# Otolith counts
load("data/dat.Rda")

# Otolith sizes
load("data/mol.Rda")

# Species-specific numerical correction factors
load("data/NCF.Rda")

# Colourblind palette
cbbPalette <- c("#009E73", "#D55E00", "#0072B2", "black")
```

# Bootstrapping

## Hierarchical extrapolation

We imputed the size and weight of unmeasured or degraded otoliths using the mean otolith length calculated from measured otoliths of the same taxon found within the same seal. In the absence of measured otoliths for a specific individual seal and prey taxon, we imputed hierarchically. First, using the mean otolith length of that taxon, from other seals sampled on the same day, and if not available, from the same month, then the same site, then the same region, and finally, from the same taxonomic family.

```{r reconstructing individual diet using wet weights prior to digestion}
# NOTE ww_mol implies input from files where otoliths were measured and equations were applied, this name is used on a rolling basis in this chunk

# Extracting inputs mol file
ww_mol <- mol %>%
             group_by(uniqueID, prey_specie) %>% 
             summarize(
                ot_measured = n(),
                meanww_ind = mean(FW),
                sumww_ind = sum(FW)) %>% ungroup()

# Merging count data with meta-data necessary extrapolation
ww <- dat
ww$site <- info$site[match(ww$uniqueID, info$uniqueID)]
ww$region <- info$region[match(ww$uniqueID, info$uniqueID)]
ww$date <- info$date[match(ww$uniqueID, info$uniqueID)]

# Fishes for which otoliths have been measured added to the wet weight data frame
ww <- merge(x = ww, y = ww_mol, by = c("uniqueID", "prey_specie"), all.x=TRUE)

# Generally, we consider that the measured otoliths were not paired as they were randomly selected, however, when the number of otoliths measured is greater than the number of prey, this implies that both otoliths for a prey individual were measured, hence in these circumstances otoliths are considered to be paired.
ww$ot_measured[is.na(ww$ot_measured)] <- 0
ww$ind_notmeasured <- ww$count - ww$ot_measured
ww$sumww <- ifelse(ww$ind_notmeasured < 0, ww$sumww_ind/2, ww$sumww_ind)

# Number of measured otoliths is also divided by two as this now implies the number of individuals. When more otoliths than prey are measured, the individuals are paired, otherwise, they are unpaired
ww$ind_measured <- ifelse(ww$ind_notmeasured < 0, round(ww$ot_measured/2, 0), ww$ot_measured)

# Recalculating after uniforming the units
ww$ind_notmeasured <- ww$count - ww$ind_measured

# Note that there are 3 for which more otoliths were measured than possible. This is an error and hence we will rather use extrapolated values and assume that none were measured 
ww$ind_notmeasured <- ifelse(ww$ind_notmeasured < 0, ww$count, ww$ind_notmeasured)

# Here above, we have assigned wet weights to those prey whose otoliths were measured. We also know the number of prey for which extrapolation will be required.

#'
#' Same Stomach
## -----------------------------------------
ww$extrap_sumww <- ww$ind_notmeasured*ww$meanww_ind

### Same day
# Extracting mol info
ww_mol <- mol 
ww_mol$date <- info$date[match(ww_mol$uniqueID, info$uniqueID)]
ww_mol <- ww_mol %>% group_by(date, prey_specie) %>% summarise(meanww_date = mean(FW)) %>% ungroup()

# Adding it to our dataframe
ww$meanww_day <- ww_mol$meanww_date[match(paste(ww$prey_specie, ww$date), paste(ww_mol$prey_specie, ww_mol$date))]

# The code below ensures that the mean is assigned correctly
ww$meanww_day <- ifelse(is.na(ww$meanww_ind), ww$meanww_day, NA) 

#Calculating sum
ww$extrap_sumww <- ifelse(!is.na(ww$meanww_day), ww$ind_notmeasured*ww$meanww_day, ww$extrap_sumww)

#'
#' Same month at same site
## -----------------------------------------

# Extracting mol info
ww_mol <- mol 
ww_mol$month <- month(info$date[match(ww_mol$uniqueID, info$uniqueID)])
ww_mol$site <- info$site[match(ww_mol$uniqueID, info$uniqueID)]
ww_mol <- ww_mol %>% group_by(site, month, prey_specie) %>% summarise(meanww_month = mean(FW)) %>% ungroup()

# Adding it to our dataframe
ww$meanww_month <- ww_mol$meanww_month[match(paste(ww$prey_specie, month(ww$date), ww$site), paste(ww_mol$prey_specie, ww_mol$month, ww_mol$site))]
# The code below ensures that the mean is assigned correctly
ww$meanww_month <- ifelse(is.na(ww$meanww_ind) & is.na(ww$meanww_day),
                          ww$meanww_month, NA) 
# Calculating sum
ww$extrap_sumww <- ifelse(!is.na(ww$meanww_month), ww$ind_notmeasured*ww$meanww_month, ww$extrap_sumww)

#'
#' Same year and site
## -----------------------------------------

# Extracting mol info
ww_mol <- mol 
ww_mol$year <- year(info$date[match(ww_mol$uniqueID, info$uniqueID)])
ww_mol$site <- info$site[match(ww_mol$uniqueID, info$uniqueID)]
ww_mol <- ww_mol %>% group_by(site, year, prey_specie) %>% summarise(meanww_year = mean(FW)) %>% ungroup()
# Adding it to our dataframe
ww$meanww_year <- ww_mol$meanww_year[match(paste(ww$prey_specie, year(ww$date), ww$site), paste(ww_mol$prey_specie, ww_mol$year, ww_mol$site))]
# The code below ensures that the mean is assigned correctly
ww$meanww_year <- ifelse(is.na(ww$meanww_ind) & is.na(ww$meanww_day) & is.na(ww$meanww_month),
                          ww$meanww_year, NA) 
# Calculating sum
ww$extrap_sumww = ifelse(!is.na(ww$meanww_year), ww$ind_notmeasured*ww$meanww_year, ww$extrap_sumww)

#'
#' Same site
## -----------------------------------------

# Extracting mol info
ww_mol <- mol 
ww_mol$site <- info$site[match(ww_mol$uniqueID, info$uniqueID)]
ww_mol <- ww_mol %>% group_by(site, prey_specie) %>% summarise(meanww_site = mean(FW)) %>% ungroup()

# Adding it to our dataframe
ww$meanww_site <- ww_mol$meanww_site[match(paste(ww$prey_specie, ww$site), paste(ww_mol$prey_specie, ww_mol$site))]

# The code below ensures that the mean is assigned correctly
ww$meanww_site <- ifelse(
    is.na(ww$meanww_ind) & is.na(ww$meanww_day) & is.na(ww$meanww_month) & is.na(ww$meanww_year),
                          ww$meanww_site, NA) 
# Calculating sum
ww$extrap_sumww <- ifelse(!is.na(ww$meanww_site), ww$ind_notmeasured*ww$meanww_site, ww$extrap_sumww)

#'
#' Same region
## -----------------------------------------

#Extracting mol info
ww_mol <- mol 
ww_mol$region <- info$region[match(ww_mol$uniqueID, info$uniqueID)]
ww_mol <- ww_mol %>% group_by(region, prey_specie) %>% summarise(meanww_region = mean(FW)) %>% ungroup()

# Adding it to our dataframe
ww$meanww_region <- ww_mol$meanww_region[match(paste(ww$prey_specie, ww$region), paste(ww_mol$prey_specie, ww_mol$region))]

# The code below ensures that the mean is assigned correctly
ww$meanww_region = ifelse(
    is.na(ww$meanww_ind) & is.na(ww$meanww_day) & is.na(ww$meanww_month) & is.na(ww$meanww_year) & is.na(ww$meanww_site),
                          ww$meanww_region, NA) 
# Calculating sum
ww$extrap_sumww <- ifelse(!is.na(ww$meanww_region), ww$ind_notmeasured*ww$meanww_region, ww$extrap_sumww)

#'
#' Same taxonomic family
## -----------------------------------------

# Extracting mol info
ww_mol <- mol 
ww_mol$prey_family <- dat$prey_family[match(ww_mol$prey_specie, dat$prey_specie)]
ww_mol <- ww_mol %>% group_by(prey_family) %>% summarise(meanww_group = mean(FW)) %>% ungroup()

# Adding it to our dataframe
ww$meanww_group <- ww_mol$meanww_group[match(ww$prey_family, ww_mol$prey_family)]

# The code below ensures that the mean is assigned correctly
ww$meanww_group <- ifelse(
    is.na(ww$meanww_ind) & is.na(ww$meanww_day) & is.na(ww$meanww_month) & is.na(ww$meanww_year) & is.na(ww$meanww_site) & is.na(ww$meanww_region),
                          ww$meanww_group, NA) 
# Calculating sum
ww$extrap_sumww <- ifelse(!is.na(ww$meanww_group), ww$ind_notmeasured*ww$meanww_group, ww$extrap_sumww)

# Total wet weight
ww$sumww[is.na(ww$sumww)] <- 0
ww$totalww <- ww$sumww+ww$extrap_sumww

# # # No extrapolations could be made for Hemithipterus americanus (Sea raven). This species occured in only one digestive tract, it hence does not contribute much to the diet. As this species belongs with the cottidae, we will assign it mean cottidae weight - https://ogsl.ca/app-guidespeces/species.jsp?id=104&lg=en

cottidae_mean <- ww_mol$meanww_group[ww_mol$prey_family == "Cottidae"]
ww$totalww <- ifelse(
  ww$prey_specie =="Hemithipterus americanus (Sea raven)", ww$ind_notmeasured*cottidae_mean,
  ww$totalww)

# Presenting the mean mass to cross-check extrapolation
meanpreymass <- ww  %>% select(prey_specie, meanww_ind, meanww_day, meanww_month, meanww_year, meanww_site, meanww_region, meanww_group)
meanpreymass <- transform(meanpreymass, acrosscolumnmean = rowMeans(meanpreymass[,-1], na.rm = TRUE)) # puts all in one columns as currently they are seperated under mean_day, month...

meanpreymass <- meanpreymass  %>% group_by(prey_specie)  %>% summarise(Avg.WetWeight_grams = mean(acrosscolumnmean))

meanpreymass$Avg.WetWeight_grams <- ifelse(
  meanpreymass$prey_specie == "Hemithipterus americanus (Sea raven)", cottidae_mean,
  meanpreymass$Avg.WetWeight_grams)

rm(cottidae_mean)# removes cottidae_mean

meanpreymass$Avg.WetWeight_grams <- round(meanpreymass$Avg.WetWeight_grams,2)
meanpreymass  %>% kable(caption = "Mean prey mass in grams")

# Preserving useful columns 
ww <- ww %>% dplyr::select(uniqueID, prey_specie, region, date, count, totalww)

# Adding metadata - age, sex, season, region
ww$sex <- info$sex[match(ww$uniqueID, info$uniqueID)]
ww$age <- info$age[match(ww$uniqueID, info$uniqueID)]
ww$season <- info$season[match(ww$uniqueID, info$uniqueID)]
ww$region_season <- paste(ww$region, ww$season, sep = "_")

# Calculating total wet weight percentage
ww <- ww %>% 
    group_by(uniqueID) %>%
    mutate(totalind = sum(totalww)) %>%
    mutate(perc_ww = 100*(totalww/totalind)) %>% ungroup()

# Rearranging columns 
ww <- ww %>%
 select(uniqueID, sex, age, region_season, date, prey_specie, count, totalww, totalind, perc_ww)

rm(ww_mol, meanpreymass)
```

## Generating uncertainty around $\%WW_{p,pooled}$ and $H_{pooled}$

To characterize uncertainty for $\%WW_{p,pooled}$ and $H_{pooled}$, we used a bootstrapping technique, with 1000 simulations. Each simulation randomly sampled the seals, with replacement, for a given region and season, and calculated $\%WW_{p,pooled}$ and $H_{pooled}$ using Equation 3 and Equation 4 from the article. The 2.5 and 97.5 percentiles of the resulting distribution were used as the 95% confidence intervals for our sample.

```{r}
#'
#' Preparing input data
## -----------------------------------------

bootprep <- function(unprepared_dataset) {
  # Select relevant columns and remove duplicates
  bootpreped <- unprepared_dataset %>%
    select(uniqueID, prey_specie, totalww) %>% 
    distinct(
      uniqueID, 
      prey_specie, 
      .keep_all = TRUE
    ) %>% 
    spread(prey_specie, totalww) # Convert to wide format
  
  # Remove uniqueID column (assumes each row corresponds to a unique individual)
  bootpreped$uniqueID <- NULL 
  
  # Replace NA values with 0
  bootpreped[is.na(bootpreped)] <- 0 
  
  return(bootpreped) # Return prepared data
}


#'
#' Resampling the population
## -----------------------------------------

resamplediet <- function(
    prepared_dataset,
    replace, 
    pool,
    proportion,
    Nresample, 
    details
) {
  
  # prepared_dataset <- bootprep(ww)
  # replace <- T
  # pool <- T
  # proportion <- 0.6
  # Nresample <- 10
  # details <- T

  
  # Calculate the effective sample size based on the proportion
  sampleffect_size <- round(nrow(prepared_dataset) * proportion)
  
  # Remove rows where the entire row is NA
  prepared_dataset <- prepared_dataset[!apply(
    prepared_dataset, 
    1, 
    function(x) all(is.na(x))
  ),] 
  
  # Create an empty matrix to store results
  out <- matrix(
    ncol = ncol(prepared_dataset), 
    nrow = Nresample
  )
  
  # Name the columns of the matrix
  colnames(out) <- paste("prop_", colnames(prepared_dataset), sep = "")
  
  # Loop through the number of resamples
  for (i in 1:Nresample) {
    
    # Set a seed for reproducibility
    set.seed(i^3 + 9 * i + 2) 
    
    # Sample rows with or without replacement
    sel <- sample(
      1:nrow(prepared_dataset), 
      sampleffect_size, 
      replace = replace
    )
    
    # Subset the data based on the sampled rows
    boot <- prepared_dataset[sel, ] 
    
    # Calculate proportions based on the pooling method
    if (pool == TRUE) {
      # Summation method: total prey_i / all prey total
      out[i, ] <- apply(boot, 2, sum) / sum(apply(boot, 2, sum))
      
      
    } else {
      # Individual mean method
      out[i, ] <- apply(
        boot %>% 
          mutate(total = rowSums(boot)) %>%
          mutate(across(everything(), ~ . / total)) %>%
          select(-total), 
        2, 
        mean
      )}
  }
  
  # Confidence intervals
  out2 <- rbind(
    apply(out, 2, quantile, probs = 0.025), # Lower 2.5% quantile
    apply(out, 2, quantile, probs = 0.975) # Upper 97.5% quantile
  )
  
  # Name the rows for clarity
  rownames(out2) <- c("lowerCI", "upperCI")
  
  
  # Mean values 
  if (pool == TRUE) {
  mean <- prepared_dataset %>%
    apply(2, sum) %>%
    `/`(sum(.)) %>%
    tibble(prey_specie = names(.), mean = .) |>
    select(prey_specie, mean) 
  } else {
    mean <- prepared_dataset %>%
      mutate(total = rowSums(.)) %>%
      mutate(across(everything(), ~ . / total)) %>%
      select(-total) |> 
      summarise(across(everything(), mean))  |> 
      pivot_longer(cols = everything(), 
                   names_to = "prey_specie", 
                   values_to = "mean") |> 
      select(prey_specie, mean)}
  
  # Convert matrix to data frame and transpose it to long format
  bootpresent <- out2 %>% 
    t() %>% 
    as.data.frame()
  
  # Add prey species column and clean up names
  bootpresent <- tibble::rownames_to_column(bootpresent, "prey_specie")
  
  bootpresent$prey_specie <- paste(
    substr(bootpresent$prey_specie, 6, nchar(bootpresent$prey_specie))
  )
  
  # Adding mean values from the dataset itself
  bootpresent$mean <- mean$mean[match(bootpresent$prey_specie, mean$prey_specie)]
  
  # Return detailed results or summary statistics based on 'details'
  if (details) {
    return(list(Resampling = out, Stats = bootpresent))
  } else {
    return(out2)
  }
}

#'
#' Preparing output format
## -----------------------------------------

touchupboot <- function(bootpresent) {
  
  # Convert proportions to percentages and round to 2 decimal places
  bootpresent <- bootpresent %>% 
    mutate_if(is.numeric, ~ . * 100) %>% 
    mutate_if(is.numeric, ~ round(., 2))
  
  # Create a formatted estimate column
  bootpresent <- bootpresent |> 
    mutate(estimate = paste0(mean, "\n[", lowerCI, ",", upperCI, "]")) |> 
    select(prey_specie, estimate)
  
  return(bootpresent) # Return formatted output
}

## Merging the three functions above
resample_to_generate_uncertainty <- function(
    unprepared_dataset, 
    grouping_column_as_string, 
    replace = TRUE, 
    pool = TRUE,
    proportion = 1,
    Nresample = 1000, 
    details = TRUE
) {
  
  # Initialize an empty data frame for storing results
  overalloutputboot <- as.data.frame(unique(unprepared_dataset$prey_specie))
  colnames(overalloutputboot) <- c("prey_specie")
  
  # Loop through each unique group in the unprepared_dataset
  unit <- as.vector(unique(unprepared_dataset[[grouping_column_as_string]])) 
  for (u in 1:length(unit)) {
    
    # Subset unprepared_dataset for the current group
    datasetmod <- unprepared_dataset[
      unprepared_dataset[[grouping_column_as_string]] == unit[u], 
    ]
    
    # Perform bootstrap re-sampling and calculate statistics
    result <- resamplediet(
      bootprep(datasetmod),
      replace, 
      pool,
      proportion,
      Nresample, 
      details
    )
    
    # Prepare the resampling results for the current group
    unitoutput <- touchupboot(result[[2]]) 
    colnames(unitoutput) <- c(
      "prey_specie", 
      paste("estimate", unit[u], proportion, sep = "_"))
    
    # Merge results into the overall output
    overalloutputboot <- merge(
      overalloutputboot, 
      unitoutput, 
      all = TRUE
    )
  }
  
  return(overalloutputboot) # Return combined results for all groups
}
```

### $\%WW_{p,pooled}$

```{r}
boot <- resample_to_generate_uncertainty(ww, "region_season")

boot %>% datatable()
```

#### Four metrics to characterise the diet

To reconstruct the populational diet composition of grey seals harvested in the waters surrounding Magdalen Islands during summer and fall sampling of 2015-2023, we used four commonly used dietary metrics derived from hard-part analysis: frequency of occurrence, numerical abundance, percent wet weight/biomass, and Shannon’s diversity index. Refer to the article for additional details on the calculation and usage of each metric.

```{r}
# Dietary behaviour: how often (FO), how much (NUM), how important (%WW)
behaviour <- dat %>%
  mutate(
    region_season = ww$region_season[match(uniqueID, ww$uniqueID)]
  )

# Extract unique sampling groups
samplinggroup <- sort(unique(behaviour$region_season))

# Initialize lists to save results and plots
plotlist <- list()
vplist <- list()
numbers_xy <- list()
numbers_pie <- list()

# Some species have long names that impede readability in the figures, we hence split their names across two lines
add_new_line_species_name <- function(species_name) {
  # Split the species name into words using a space as the delimiter
  words <- strsplit(species_name, " ")[[1]]
  
  if (length(words) > 1) {
    # If the species name has more than one word:
    # Combine the first and second words with a newline separator
    modified_name <- paste(words[1], words[2], sep = "\n")
  } else {
    # If the species name has only one word, keep it unchanged
    modified_name <- species_name
  }
  
  # Return the modified species name
  return(modified_name)
}

for (s in 1:length(samplinggroup)) {
  
  # Frequency of Occurrence (FO)
  group <- behaviour %>%
    filter(region_season == paste0(samplinggroup[s]))
  
  FO <- group %>%
    group_by(prey_specie) %>%
    summarise(
      n.dt = n(),
      FO = 100 * (n.dt / length(unique(group$uniqueID))),
      N.Abundance = sum(count)  # Used later for numerical abundance
    ) %>%
    ungroup()
  
  # Numerical abundance
  prey <- unique(group$prey_specie)
  
  # Empty dataframe for numerical abundance calculation
  count_for_abundance <- NULL
  for (p in 1:length(prey)) {
    unique_extract <- subset(group, prey_specie == prey[p])
    unique_extract <- unique(unique_extract$uniqueID)
    sub <- group %>%
      filter(uniqueID %in% unique_extract)
    total.count <- sum(sub$count)
    
    out <- data.frame(
      prey_specie = prey[p],
      total.count
    )
    
    count_for_abundance <- rbind(count_for_abundance, out)
  }
  
  # Add total count and calculate percent abundance
  FO$total.count <- count_for_abundance$total.count[
    match(FO$prey_specie, count_for_abundance$prey_specie)
  ]
  FO$percentabundance <- (FO$N.Abundance / FO$total.count) * 100
  
  # Percent wet weight
  percwwpergroup <- boot %>%
    select(matches(paste0('prey_specie|', samplinggroup[s]))) %>%
    # Extract mean, lower CI, and upper CI
    mutate(
      mean = str_extract(
        !!sym(paste0("estimate_", samplinggroup[s], "_1")),
        "^[^\\n]+"
      ),
      CI = str_extract(
        !!sym(paste0("estimate_", samplinggroup[s], "_1")),
        "\\[.*\\]"
      ),
      lCI = str_extract(CI, "(?<=\\[)[^,]+"),
      uCI = str_extract(CI, "(?<=,)[^\\]]+")
    ) %>%
    mutate(
      mean = as.numeric(mean),
      lCI = as.numeric(lCI),
      uCI = as.numeric(uCI)
    ) %>%
    select(-CI)
  
  # Merge FO and numerical abundance
  percwwpergroup$FO <- FO$FO[
    match(percwwpergroup$prey_specie, FO$prey_specie)
  ]
  percwwpergroup$NUM <- FO$percentabundance[
    match(percwwpergroup$prey_specie, FO$prey_specie)
  ]
  
  # Remove rows with NA means
  percwwpergroup <- percwwpergroup %>%
    filter(!is.na(mean))
  
  # Add lower and upper limits
  percwwpergroup$lower <- percwwpergroup$lCI
  percwwpergroup$upper <- percwwpergroup$uCI
  
  # Identify top three contributors
  first_three_contributors <- percwwpergroup %>%
    arrange(desc(mean)) %>%
    head(3) %>%
    select(prey_specie)
  
  # Highlight top three contributors
  percwwpergroup$highlight <- ifelse(
    percwwpergroup$prey_specie %in% first_three_contributors$prey_specie,
    "yes",
    "no"
  )
  
  # Simplify species names for plotting
  percwwpergroup$prey_specie <- str_extract_all(
    percwwpergroup$prey_specie, "\\([^()]+\\)"
  )
  percwwpergroup$prey_specie <- substring(
    percwwpergroup$prey_specie, 2, nchar(percwwpergroup$prey_specie) - 1
  )
  
  # Add prey type
  percwwpergroup$type <- NCF$type[
    match(percwwpergroup$prey_specie, NCF$common_name)
  ]
  
  # Apply line-breaking function to species names
  percwwpergroup$prey_specie <- sapply(
    percwwpergroup$prey_specie,
    add_new_line_species_name
  )
  
  # Save processed data
  numbers_xy[[s]] <- percwwpergroup
  
  # Remove zero means
  percwwpergroup <- percwwpergroup %>%
    filter(mean != 0)
  
  # Plot bubble plot
  plotlist[[s]] <- ggplot() +
    geom_point(
      data = percwwpergroup[percwwpergroup$highlight == "no", ],
      aes(x = FO, y = mean, col = type, size = NUM),
      pch = 19, alpha = 0.3
    ) +
    geom_errorbar(
      data = percwwpergroup[percwwpergroup$highlight == "yes", ],
      aes(x = FO, y = mean, ymin = lower, ymax = upper),
      width = 1, col = "black"
    ) +
    geom_point(
      data = percwwpergroup[percwwpergroup$highlight == "yes", ],
      aes(x = FO, y = mean, col = type, size = NUM),
      pch = 19, alpha = 0.9
    ) +
    scale_size(
      breaks = c(1, 10, 20, 40, 60, 80),
      limits = c(0, 100),
      range = c(0.5, 10)
    ) +
    # ggrepel::geom_text_repel(
    #   data = percwwpergroup[percwwpergroup$highlight == "yes", ],
    #   aes(FO, upper + 0.08, label = prey_specie),
    #   direction = "x",
    #   box.padding = 0.1,
    #   point.padding = 0.1,
    #   segment.color = NA,
    #   size = 5,
    #   force = 0.5,
    #   force_pull = 0.1,
    #   max.time = 2,
    #   seed = 1234
    # ) +
    geom_text(
      data = subset(percwwpergroup, highlight == "yes"),
      aes(
        x = FO, 
        y = ifelse(prey_specie == "Atlantic\nherring", 
                   upper + 2, upper + 1), 
        label = prey_specie),
      vjust = 0,
      size = 5) +
    xlim(0, 100) +
    ylim(0, 100) +
    labs(
      x = NULL,
      y = NULL,
      title = ifelse(
        samplinggroup[s] == "M.Islands_Fall", "Magdalen Islands (Fall)",
        ifelse(
          samplinggroup[s] == "M.Islands_Summer", "Magdalen Islands (Summer)",
          ifelse(
            samplinggroup[s] == "M.Bay_Fall", "Miramichi Bay (Fall)",
            "Northumberland Strait (Fall)"
          )
        )
      ),
      size = "Prey-specific \nNumerical Abundance (%)",
      col = "Functional Group"
    ) +
    scale_colour_manual(values = cbbPalette) +
    theme_bw() +
    theme(
      plot.title = element_text(
        hjust = 0.6, size = 16), 
      axis.text = element_text(size = 14), 
      legend.text = element_text(size = 14), 
      legend.title = element_text(size = 14))
  
  # Pie chart for functional group contribution
  funcgroup <- percwwpergroup %>%
    group_by(type) %>%
    summarise(contribution = sum(mean)) %>%
    ungroup()
  
  numbers_pie[[s]] <- funcgroup
  
  vplist[[s]] <- ggplot(data = funcgroup, aes(x = "", y = contribution, fill = type)) +
    geom_col(position = "fill") +
    coord_polar(theta = "y", start = 0) +
    scale_fill_manual(values = cbbPalette) +
    guides(fill = "none") +
    theme_void()
}

# Figures for manuscript

# Magdalen Islands
figMaggies <- ggarrange(
  plotlist[[3]], plotlist[[2]],
  align = 'h', common.legend = TRUE, legend = "top",
  labels = c("A", "B")
)

figMaggiesAxes <- annotate_figure(
  figMaggies,
  left = textGrob("Percent Wet-Weight (%)", rot = 90, hjust = 0.65, gp = gpar(cex = 1.3)),
  bottom = textGrob("Frequency of Occurrence (%)", hjust = 0.38, gp = gpar(cex = 1.3))
)

figMaggiesAxesPies <- ggdraw() +
  draw_plot(figMaggiesAxes, x = 0, y = 0, width = 1, height = 1) +
  draw_plot(vplist[[3]], x = 0.05, y = 0.55, width = 0.20, height = 0.20) +
  draw_plot(vplist[[2]], x = 0.537, y = 0.55, width = 0.20, height = 0.20)

ggsave(
  "../4_MANUSCRIPT/output/figures/diet_maggies.png",
  figMaggiesAxesPies,
  bg = "white",
  width = 10, height = 8, dpi = 600
)

ggsave(
  "../4_MANUSCRIPT/output/figures/Figure2.tif",
  figMaggiesAxesPies,
  bg = "white",
  width = 10, height = 8, dpi = 600
)

# Fall plots
figFall <- ggarrange(
  plotlist[[2]], plotlist[[1]], plotlist[[4]],
  ncol = 3, align = 'h', common.legend = TRUE, legend = "top",
  labels = c("A", "B", "C")
)

figFallAxes <- annotate_figure(
  figFall,
  left = textGrob("Percent Wet-Weight (%)", rot = 90, hjust = 0.65, gp = gpar(cex = 1.3)),
  bottom = textGrob("Frequency of Occurrence (%)", hjust = 0.38, gp = gpar(cex = 1.3))
)

figFallAxesPies <- ggdraw() +
  draw_plot(figFallAxes, x = 0, y = 0, width = 1, height = 1) +
  draw_plot(vplist[[2]], x = 0.05, y = 0.62, width = 0.18, height = 0.18) +
  draw_plot(vplist[[1]], x = 0.37, y = 0.62, width = 0.18, height = 0.18) +
  draw_plot(vplist[[4]], x = 0.70, y = 0.62, width = 0.18, height = 0.18)

ggsave(
  "../4_MANUSCRIPT/output/figures/diet_fall.png",
  figFallAxesPies,
  bg = "white",
  width = 10, height = 8, dpi = 600
)

ggsave(
  "../4_MANUSCRIPT/output/figures/Figure3.tif",
  figFallAxesPies,
  bg = "white",
  width = 10, height = 8, dpi = 600
)
```

### $H_{pooled}$

```{r}
PopShannonEstimate <- function(data) {
  # Calculate Shannon index and 95% CI for diet proportions
  
  # Calculate mean Shannon index
  mean <- bootprep(data) %>%
    apply(2, sum) %>%
    `/`(sum(.)) %>%
    tibble(prey_specie = names(.), mean = .) %>%
    summarise(
      H = -sum(mean * log(mean)) %>%
        round(2)
    )
  
  # Bootstrap to estimate confidence intervals
  CI <- resamplediet(
    bootprep(data),
    replace = TRUE,
    pool = TRUE,
    proportion = 1,
    Nresample = 1000,
    details = TRUE
  )[[1]] %>%
    data.frame() %>%
    mutate_if(is.numeric, ~ . * log(.)) %>%
    rowwise() %>%
    mutate(
      Shannon = -sum(c_across(everything()), na.rm = TRUE)
    ) %>%
    select(Shannon) %>%
    ungroup() %>%
    summarise(
      lCI = quantile(Shannon, probs = c(0.025)) %>%
        round(2),
      uCI = quantile(Shannon, probs = c(0.975)) %>%
        round(2)
    ) %>%
    transmute(
      Prey = "Shannon Index",
      WW = paste0(mean, " [", lCI, ",", uCI, "]")
    ) %>%
    data.frame()
  
  return(CI)
}

# Initialize list for summary tables
summaries <- list()

for (s in 1:length(samplinggroup)) {
  
  group_contribution <- numbers_pie[[s]] %>%
    data.frame()
  
  # Create summary table for each sampling group
  table <- bind_rows(
    numbers_xy[[s]] %>%
      select(
        Prey = prey_specie,
        WW = mean, lCI, uCI,
        FO, NUM, Group = type
      ) %>%
      mutate(
        FO = round(FO, 1),
        NUM = round(NUM, 1),
        WW = paste0(WW, " [", lCI, ",", uCI, "]"),
        lCI = NULL,
        uCI = NULL
      ) %>%
      arrange(Prey),
    
    PopShannonEstimate(
      ww %>%
        filter(region_season == samplinggroup[s])
    )
  ) %>%
    mutate(
      contribution = group_contribution$contribution[
        match(Group, group_contribution$type)
      ]
    )
  
  summaries[[as.character(samplinggroup[s])]] <- table
}

# Save summary results
save(
  summaries,
  file = "../4_MANUSCRIPT/output/tables/bootstrapping_summaries.Rda"
)
```

```{r}
# Saving files for manuscript
save(mol, file = "../4_MANUSCRIPT/output/tables/mol.Rda")

save(info, file = "../4_MANUSCRIPT/output/tables/info.Rda")

save(NCF, file = "../4_MANUSCRIPT/output/tables/NCF.Rda")

save(ww, file = "output/Dataframes/ww.Rda")
```

### $\%WW_{p,individual}$

An alternative method to calculate the relative importance of prey taxa in digestive tracts, in place of using pooled diet estimates, is to use individual mean diet estimates (see supplementary materials). This approach calculates the percent contribution of each prey taxon for each individual seal, then averages these values across all sampled individuals to provide the relative importance of prey in an average digestive track.

```{r}
individual_diet_reconstruction <- resample_to_generate_uncertainty(
  ww, 
  "region_season",
  pool = F
  )

save(individual_diet_reconstruction, file = "../4_MANUSCRIPT/output/tables/individual_diet_reconstruction.Rda")

rm(list = ls())
```
