---
title: "Modeling"
format: html
editor: visual
---

# Model preparation

```{r}
# Package names
packages <- c(
  # import data
  "readr",
  "readxl",
  "openxlsx",
  
  # syntax
  "plyr",
  "dplyr",
  "tidyverse",
  
  # cleaning 
  "janitor", 
  "broom",
  
  # date 
  "lubridate",
  
  # graphs 
  "ggplot2",
  "ggrepel",
  "ggsignif",
  "gridExtra",
  "ggpubr",
  "plotly",
  "scales",
  "cowplot",
  "magick",
  "ggeffects",
  "patchwork", 
  
  # stats
  "glmmTMB",
  "effects",
  "emmeans",
  "DHARMa",
  "betareg",
  
  # tables
  "DT",
  
  # knit 
  "knitr",
  
  # spatial data
  "sf", # spatial maipulation
  "tmap", # map making
  "grid", # viewport
  
  # string manipulation 
  "stringr")

# Install packages not yet installed
installed_packages <- packages %in% rownames(installed.packages())
if (any(installed_packages == FALSE)) {
  install.packages(packages[!installed_packages])
}

# Packages loading
invisible(lapply(packages, library, character.only = TRUE))

rm(installed_packages, packages)
```

To investigate inter-individual variability, across age-sex groups and year, in prey diversity, prey occurrence and its relative importance when present (objective III), we first subsetted our data to only include summer sampling at Magdalen Islands, between 2017 to 2023, because it represented the largest and most consistent sampling group, with reasonable sample size within each year.

```{r Preparing modeling dataframes}
# Wet weight estimates from measured otoliths and extrapolated wet weights from unmeasured or degraded otoliths
load("output/Dataframes/ww.Rda")

# Model dataframe
ww <- ww %>%
        filter(region_season == "M.Islands_Summer", year(date) %in% c(2017:2023)) %>%
        mutate(
          perc_ww = as.numeric(perc_ww), 
          sexChr = as.character(sex),
          sex = as.factor(sex),
          age = as.numeric(age), 
          yearChr = as.character(year(date)), 
          year = as.factor(yearChr),
          totalind = as.numeric(totalind),
          date = as.factor(date), 
          agegroupChr = ifelse(age < 1, "Yearling",
                        ifelse(age > 4 & sexChr == "F", "Adult Female",
                        ifelse(age > 4 & sexChr == "M", "Adult Male", "Juvenile"))), 
          agegroup = as.factor(agegroupChr),
          agegroup = factor(agegroup, levels = c("Yearling", "Juvenile", "Adult Female", "Adult Male")), 
          region_season = NULL
        )

# removing NA values for model comparaison
sapply(ww, function(x)any(is.na(x)))
ww <- ww %>% filter(!is.na(agegroup))

# Converting model dataframe to presence dataframe
presence <- ww %>% 
              mutate( 
                count = NULL, 
                age = NULL, 
                totalww = NULL, 
                perc_ww = 1) %>% 
              spread(prey_specie, perc_ww) %>% 
              replace(. , is.na(.) , 0) # a simple replace because all other columns do not have NA values hence it is restricted to the presence columns
```

Despite consuming a variety of prey taxa, only a few prey taxa contribute to the majority of grey seal diet. During the summer sampling at Magdalen Islands, sand lance (*Ammodyctes sp.*), cod (*Gadus morhua*), and capelin (*Mallotus villosus*) accounted for about 90% of the total diet by weight ($\%WW_p$). Given the substantial contribution of the percent wet weight of the three taxa, we modelled their occurrence (presence/absence) and relative importance (%WW), when present.

```{r}
# We model major species identified in Part I at Magdalen Islands in the Summer, sample sizes for which are 
ww %>%
    filter(prey_specie %in% c("Ammodytes sp. (Sand lance)", "Gadus sp. (Cod)", "Mallotus villosus (Capelin)")) %>%
    count(prey_specie)  %>% 
    datatable(., rownames = T)

# correcting for column names to simplyfy model creation
names(presence)[names(presence) == 'Ammodytes sp. (Sand lance)'] <- 'sandlance'
names(presence)[names(presence) == 'Gadus sp. (Cod)'] <- 'cod'
names(presence)[names(presence) == 'Mallotus villosus (Capelin)'] <- 'capelin'
```

## Occurrence model

```{r}
occurrencemodeling <- function(
  response_var, 
  data, 
  n_iterations = 1000
) {
  
  # response_var <- "sandlance"
  # data <- presence
  
  # Define formula for the model
  formula <- as.formula(paste(response_var, "~ agegroup + year"))
  
  # Fit a binomial GLM
  binom <- glm(
    formula, 
    family = binomial(), 
    data = data
  )
  
  # Extract model summary
  model_summary <- summary(binom)
  
  ## Occurrence by year
  formula_emm <- as.formula("pairwise ~ year")
  
  # Compute estimated marginal means (EMMs) for year
  predictions_year <- emmeans(
    binom, 
    formula_emm, 
    adjust = "tukey", 
    type = "response", 
    weights = "equal"
  )$emmeans %>% 
    data.frame()
  
  # Perform pairwise comparisons with Tukey adjustment
  comparaisons <- emmeans(
    binom, 
    formula_emm, 
    adjust = "tukey", 
    type = "response", 
    weights = "equal"
  )$contrasts %>% 
    data.frame() 
  
  pairwise <- comparaisons %>% 
    filter(p.value <= 0.05)
  
  # Extract significant pairs for plotting
  pairwise_graph <- pairwise |>  
    separate(contrast, c("var1", "var2"), extra = "merge") 
  
  pairwise_graph$var1 <- gsub("year", "", pairwise_graph$var1) %>% as.character()
  pairwise_graph$var2 <- gsub("year", "", pairwise_graph$var2) %>% as.character()
  
  pairs <- lapply(
    1:nrow(pairwise_graph), 
    function(i) list(c(pairwise_graph$var1[i], pairwise_graph$var2[i]))
  ) 
  
  pairs <- unlist(pairs, recursive = FALSE) # Flatten list
  
  position <- seq(
    from = max(predictions_year$asymp.UCL) + 0.05, 
    to = max(predictions_year$asymp.UCL) + 0.05 + 0.05 * nrow(pairwise_graph), 
    by = 0.05
  )
  
  # Generate occurrence plot by year
  year_plot <- ggplot() +
    geom_jitter(
      data = data, 
      aes(x = year, y = !!sym(response_var)), 
      col = "grey", alpha = 0.8, 
      width = 0.2, height = 0.1
    ) +
    geom_errorbar(
      data = predictions_year, 
      aes(x = year, ymin = asymp.LCL, ymax = asymp.UCL), 
      width = 0.2
    ) + 
    geom_point(
      data = predictions_year, 
      aes(x = year, y = prob), 
      size = 3
    ) + 
    labs(
      x = NULL, 
      y = "Presence probability"
    ) +
    theme_bw() + 
    scale_y_continuous(breaks = seq(0, 1, by = 0.25)) + 
    geom_signif(
      data = predictions_year,
      aes(x = year, y = prob),
      comparisons = pairs,
      annotation = "",
      map_signif_level = TRUE,
      textsize = 7, 
      y_position = position, 
      col = "black"
    ) + 
    theme(
      axis.text = element_text(size = 10), 
      axis.title = element_text(size = 14))
  
  ## Occurrence by agegroup
  formula_emm <- as.formula("pairwise ~ agegroup")
  
  predictions_agegroup <- emmeans(
    binom, 
    formula_emm, 
    adjust = "tukey", 
    type = "response", 
    weights = "equal"
  )$emmeans %>% 
    data.frame()
  
  comparaisons_agegroup <- emmeans(
    binom, 
    formula_emm, 
    adjust = "tukey", 
    type = "response", 
    weights = "equal"
  )$contrasts %>%  
    data.frame() 
  
  pairwise_agegroup <- comparaisons_agegroup %>% 
    filter(p.value <= 0.05)
  
  pairwise_graph <- pairwise_agegroup |>  
    separate(contrast, c("var1", "var2"), extra = "merge")
  
  pairwise_graph$var1 <- gsub("agegroup", "", pairwise_graph$var1) %>% as.character()
  pairwise_graph$var2 <- gsub("agegroup", "", pairwise_graph$var2) %>% as.character()
  
  pairs_agegroup <- lapply(
    1:nrow(pairwise_graph), 
    function(i) list(c(pairwise_graph$var1[i], pairwise_graph$var2[i]))
  )
  
  pairs_agegroup <- unlist(pairs_agegroup, recursive = FALSE)
  
  position_agegroup <- seq(
    from = max(predictions_agegroup$asymp.UCL) + 0.05, 
    to = max(predictions_agegroup$asymp.UCL) + 0.05 + 0.05 * nrow(pairwise_graph), 
    by = 0.05
  )
  
  # Generate occurrence plot by agegroup
 agegroup_plot <- ggplot() +
    geom_jitter(
      data = data, 
      aes(x = agegroup, y = !!sym(response_var)), 
      col = "grey", alpha = 0.8, 
      width = 0.2, height = 0.1
    ) +
    geom_errorbar(
      data = predictions_agegroup, 
      aes(x = agegroup, ymin = asymp.LCL, ymax = asymp.UCL), 
      width = 0.2
    ) + 
    geom_point(
      data = predictions_agegroup, 
      aes(x = agegroup, y = prob), 
      size = 3
    ) + 
    labs(
      x = NULL, 
      y = "Presence probability"
    ) +
    theme_bw() + 
    scale_y_continuous(breaks = seq(0, 1, by = 0.25)) + 
    geom_signif(
      data = predictions_agegroup,
      aes(x = agegroup, y = prob),
      comparisons = pairs_agegroup,
      annotation = "",
      map_signif_level = TRUE,
      textsize = 7, 
      y_position = position_agegroup, 
      col = "black"
    )  + 
    theme(
      axis.text = element_text(size = 10), 
      axis.title = element_text(size = 14))
  
  # Combine plots
  fig <- (year_plot) + (agegroup_plot + labs(y = NULL))
  
  # Combine significant pairwise comparisons
  signif <- rbind.fill(comparaisons, comparaisons_agegroup)

  # Residuals 
  residuals <- simulateResiduals(fittedModel = binom, 
                                   n = n_iterations,
                                   plot = F)
  
  # Return results as a list
  return(list(
    model_summary, 
    fig, 
    predictions_year,
    predictions_agegroup,
    signif,
    binom, 
    data, 
    residuals
  ))
}
```

## Consumption model

```{r}
consumpmodeling <- function(
  prey_taxon, 
  n_simulations = 1000
) {
  
  # prey_taxon <- "Ammodytes sp. (Sand lance)"
  
  data <- ww %>% 
            filter(prey_specie == prey_taxon) %>% 
            mutate(
              prop = perc_ww/100,
              restricted_prop =
                (((prop)*(nrow(.)-1)) + 0.5) /
                nrow(.))
  
  response_var <- "restricted_prop"
  
  # Define formula for the model
  formula <- as.formula(paste(response_var, "~ agegroup + year"))
  
  # Model 
  beta <- betareg(formula,
             data = data,
             link = c("logit"),
             link.phi = NULL,
             type = c("ML"))
  
  # Extract model summary
  model_summary <- summary(beta)
  
  ## Occurrence by year
  formula_emm <- as.formula("pairwise ~ year")
  
  # Compute estimated marginal means (EMMs) for year
  predictions_year <- emmeans(
    beta, 
    formula_emm, 
    adjust = "tukey", 
    type = "response", 
    weights = "equal"
  )$emmeans %>% 
    data.frame() %>%  
  mutate(
    emmean = 
      100*(emmean*nrow(data) - 0.5)/(nrow(data)-1),
    asymp.LCL = 
      (asymp.LCL*nrow(data) - 0.5)/(nrow(data)-1), 
    asymp.UCL = 
      (asymp.UCL*nrow(data) - 0.5)/(nrow(data)-1),
    asymp.LCL = 
      ifelse(asymp.LCL < 0, 0, asymp.LCL*100),
    asymp.UCL = 
      ifelse(asymp.UCL > 1, 100, asymp.UCL*100))
  
  # Perform pairwise comparisons with Tukey adjustment
  comparaisons <- emmeans(
    beta, 
    formula_emm, 
    adjust = "tukey", 
    type = "response", 
    weights = "equal"
  )$contrasts %>% 
    data.frame() 
  
  pairwise <- comparaisons %>% 
    filter(p.value <= 0.05)
  
  # Extract significant pairs for plotting
  pairwise_graph <- pairwise |>  
    separate(contrast, c("var1", "var2"), extra = "merge") 
  
  pairwise_graph$var1 <- gsub(
    "year", "", pairwise_graph$var1) %>% as.character()
  pairwise_graph$var2 <- gsub(
    "year", "", pairwise_graph$var2) %>% as.character()
  
  pairs <- lapply(
    1:nrow(pairwise_graph), 
    function(i) list(c(pairwise_graph$var1[i], pairwise_graph$var2[i]))
  ) 
  
  pairs <- unlist(pairs, recursive = FALSE) # Flatten list
  
  position <- seq(
    from = max(predictions_year$asymp.UCL) + 5, 
    to = max(predictions_year$asymp.UCL) + 5 + 5 * nrow(pairwise_graph), 
    by = 5
  )
  
  # Generate importance plot by year
  year_plot <- ggplot() +
    geom_jitter(
      data = data, 
      aes(x = year, y = perc_ww), 
      col = "grey", alpha = 0.8, 
      width = 0.2, height = 0
    ) +
    geom_errorbar(
      data = predictions_year, 
      aes(x = year, ymin = asymp.LCL, ymax = asymp.UCL), 
      width = 0.2
    ) + 
    geom_point(
      data = predictions_year, 
      aes(x = year, y = emmean), 
      size = 3
    ) + 
    labs(
      x = NULL, 
      y = "Percent Wet Weight"
    ) +
    theme_bw() + 
    scale_y_continuous(breaks = seq(0, 100, by = 25)) + 
    geom_signif(
      data = predictions_year,
      aes(x = year, y = emmean),
      comparisons = pairs,
      annotation = "",
      map_signif_level = TRUE,
      textsize = 7, 
      y_position = position, 
      col = "black"
    )  + 
    theme(
      axis.text = element_text(size = 10), 
      axis.title = element_text(size = 14))
  
  ## Occurrence by agegroup
  formula_emm <- as.formula("pairwise ~ agegroup")
  
  predictions_agegroup <- emmeans(
    beta, 
    formula_emm, 
    adjust = "tukey", 
    type = "response", 
    weights = "equal"
  )$emmeans %>% 
    data.frame() %>% 
  mutate(
    emmean = 100*(emmean*nrow(data) - 0.5)/(nrow(data)-1),
    asymp.LCL = (asymp.LCL*nrow(data) - 0.5)/(nrow(data)-1), 
    asymp.UCL = (asymp.UCL*nrow(data) - 0.5)/(nrow(data)-1),
    asymp.LCL = ifelse(asymp.LCL < 0, 0, asymp.LCL*100),
    asymp.UCL = ifelse(asymp.UCL > 1, 100, asymp.UCL*100))
  
  comparaisons_agegroup <- emmeans(
    beta, 
    formula_emm, 
    adjust = "tukey", 
    type = "response", 
    weights = "equal"
  )$contrasts %>%  
    data.frame() 
  
  
  pairwise_agegroup <- comparaisons_agegroup %>% 
    filter(p.value <= 0.05)
  
  pairwise_graph <- pairwise_agegroup |>  
    separate(contrast, c("var1", "var2"), extra = "merge")
  
  pairwise_graph$var1 <- gsub("agegroup", "", pairwise_graph$var1) %>% as.character()
  pairwise_graph$var2 <- gsub("agegroup", "", pairwise_graph$var2) %>% as.character()
  
  pairs_agegroup <- lapply(
    1:nrow(pairwise_graph), 
    function(i) list(c(pairwise_graph$var1[i], pairwise_graph$var2[i]))
  )
  
  pairs_agegroup <- unlist(pairs_agegroup, recursive = FALSE)
  
  position_agegroup <- seq(
    from = max(predictions_agegroup$asymp.UCL) + 5, 
    to = max(predictions_agegroup$asymp.UCL) + 5 + 5 * nrow(pairwise_graph), 
    by = 5
  )
  
  # Generate occurrence plot by agegroup
 agegroup_plot <- ggplot() +
    geom_jitter(
      data = data, 
      aes(x = agegroup, y = perc_ww), 
      col = "grey", alpha = 0.8, 
      width = 0.2, height = 0
    ) +
    geom_errorbar(
      data = predictions_agegroup, 
      aes(x = agegroup, ymin = asymp.LCL, ymax = asymp.UCL), 
      width = 0.2
    ) + 
    geom_point(
      data = predictions_agegroup, 
      aes(x = agegroup, y = emmean), 
      size = 3
    ) + 
    labs(
      x = NULL, 
      y = "Percent Wet Weight"
    ) +
    theme_bw() + 
    scale_y_continuous(breaks = seq(0, 100, by = 25)) + 
    geom_signif(
      data = predictions_agegroup,
      aes(x = agegroup, y = emmean),
      comparisons = pairs_agegroup,
      annotation = "",
      map_signif_level = TRUE,
      textsize = 7, 
      y_position = position_agegroup, 
      col = "black"
    )  + 
    theme(
      axis.text = element_text(size = 10), 
      axis.title = element_text(size = 14))
  
  # Combine plots
  fig <- (year_plot) + (agegroup_plot + labs(y = NULL))
  
  # Combine significant pairwise comparisons
  signif <- rbind.fill(comparaisons, comparaisons_agegroup)
  
  # Residuals
  residuals <- createDHARMa(
    simulatedResponse = as.matrix(
      simulate(beta, nsim = n_simulations)), 
    observedResponse = data$restricted_prop, 
    fittedPredictedResponse = predict(beta))
  
  # Return results as a list
  return(list(
    model_summary, 
    fig, 
    predictions_year,
    predictions_agegroup,
    signif,
    beta, 
    data, 
    residuals
  ))
}
```

```{r}
occur_sandlance <- occurrencemodeling("sandlance", presence) 
consump_sandlance <- consumpmodeling("Ammodytes sp. (Sand lance)")

save(occur_sandlance, file = "../4_MANUSCRIPT/output/figures/presence_sandlance.Rda")
save(consump_sandlance, file = "../4_MANUSCRIPT/output/figures/comsumption_sandlance.Rda")
```

```{r}
occur_cod <- occurrencemodeling("cod", presence)
consump_cod <- consumpmodeling("Gadus sp. (Cod)")

save(occur_cod, file = "../4_MANUSCRIPT/output/figures/presence_cod.Rda")
save(consump_cod, file = "../4_MANUSCRIPT/output/figures/comsump_cod.Rda")
```

```{r}
occur_capelin <- occurrencemodeling("capelin", presence)
consump_capelin <- consumpmodeling("Mallotus villosus (Capelin)")



save(occur_capelin, file = "../4_MANUSCRIPT/output/figures/presence_capelin.Rda")
save(consump_capelin, file = "../4_MANUSCRIPT/output/figures/consump_capelin.Rda")
```

## Diversity Model

Unlike seasonal and regional comparisons, where local prey assemblages may differ, absences among samples collected in the same season (summer 2017–2023) and region (Magdalen Islands) can result from lack of predator–prey encounter, failure to detect, or failure to capture, and thus do not necessarily indicate true absence — particularly given the lack of evidence for local extirpations in the region during the study period. Allowing species richness to vary would implicitly assume that an absence in a given sample represents true absence. To avoid this assumption, we assume the contrary - that at least one individual (the minimum requirement for species richness) of each prey taxon found in the digestive tracts was present near the Magdalen Island colonies throughout the study period. Mathematically, we treated species richness as constant, excluded it from the model by dividing the Shannon diversity index by its maximum possible value, and focused solely on evenness (i.e. feeding behaviour; predation of single or multiple prey taxa). The maximum achievable Shannon value is the logarithm value of the total number of unique prey taxa found in all digestive tracts, i.e. log(21), where zero represents single prey consumption (no diversity) and one represents equal consumption in biomass of all 21 prey taxa (maximum achievable diversity). This approach, known as the Shannon equity index ($H'_s$), enabled us to assess changes in prey composition without conflating them with potential artefacts of detection or capture.

```{r}
### Using biomass
diversity <- ww %>%
        dplyr::select(uniqueID,agegroup,sex,year,prey_specie,perc_ww, date, totalind) %>%
        mutate(
          prop = perc_ww/100,
          perc_ww = NULL,
          mediantotalind = as.character(totalind - median(totalind)/1000),
          totalind = as.character(totalind)) %>%
        spread(prey_specie,prop) %>%
        replace(is.na(.), 0) %>%
        mutate_if(is.numeric, ~.*log(.)) %>%
        mutate(
          shannon = -rowSums(
            across(
              all_of(
                unique(ww$prey_specie))), na.rm = T),
          medianTotalInd = as.numeric(mediantotalind),
          totalind = as.numeric(totalind),
          shannonEquity = shannon/log(21)) # 21 prey species
```

```{r}
diversitymodeling <- function(
  diversity_dataframe, 
  n_simulations = 1000) {
  
  diversity_dataframe <- diversity
  
  data <- diversity_dataframe %>% 
            mutate(
              restricted_prop =
                (((shannonEquity)*(nrow(.)-1)) + 0.5) /
                nrow(.))
  
  response_var <- "restricted_prop"
  
  # Define formula for the model
  formula <- as.formula(paste(response_var, "~ agegroup + year"))
  
  # Model 
  beta <- betareg(formula,
              data = data,
              link = c("logit"),
              link.phi = NULL,
              type = c("ML"))
  
  # Extract model summary
  model_summary <- summary(beta)
  
  ## Occurrence by year
  formula_emm <- as.formula("pairwise ~ year")
  
  # Compute estimated marginal means (EMMs) for year
  predictions_year <- emmeans(
    beta, 
    formula_emm, 
    adjust = "tukey", 
    type = "response", 
    weights = "equal"
  )$emmeans %>% 
    data.frame() %>%  
  mutate(
    emmean = 
      (emmean*nrow(data) - 0.5)/(nrow(data)-1),
    asymp.LCL = 
      (asymp.LCL*nrow(data) - 0.5)/(nrow(data)-1), 
    asymp.UCL = 
      (asymp.UCL*nrow(data) - 0.5)/(nrow(data)-1),
    asymp.LCL = 
      ifelse(asymp.LCL < 0, 0, asymp.LCL),
    asymp.UCL = 
      ifelse(asymp.UCL > 1, 1, asymp.UCL))
  
  # Perform pairwise comparisons with Tukey adjustment
  comparaisons <- emmeans(
    beta, 
    formula_emm, 
    adjust = "tukey", 
    type = "response", 
    weights = "equal"
  )$contrasts %>% 
    data.frame() 
  
  pairwise <- comparaisons %>% 
    filter(p.value <= 0.05)
  
  # Extract significant pairs for plotting
  pairwise_graph <- pairwise |>  
    separate(contrast, c("var1", "var2"), extra = "merge") 
  
  pairwise_graph$var1 <- gsub(
    "year", "", pairwise_graph$var1) %>% as.character()
  pairwise_graph$var2 <- gsub(
    "year", "", pairwise_graph$var2) %>% as.character()
  
  pairs <- lapply(
    1:nrow(pairwise_graph), 
    function(i) list(c(pairwise_graph$var1[i], pairwise_graph$var2[i]))
  ) 
  
  pairs <- unlist(pairs, recursive = FALSE) # Flatten list
  
  position <- seq(
    from = max(predictions_year$asymp.UCL) + 0.05, 
    to = max(predictions_year$asymp.UCL) + 0.05 + 0.05 * nrow(pairwise_graph), 
    by = 0.05
  )
  
  # Generate importance plot by year
  year_plot <- ggplot() +
    geom_jitter(
      data = data, 
      aes(x = year, y = shannonEquity), 
      col = "grey", alpha = 0.8, 
      width = 0.2, height = 0
    ) +
    geom_errorbar(
      data = predictions_year, 
      aes(x = year, ymin = asymp.LCL, ymax = asymp.UCL), 
      width = 0.2
    ) + 
    geom_point(
      data = predictions_year, 
      aes(x = year, y = emmean), 
      size = 3
    ) + 
    labs(
      x = NULL, 
      y = "Shannon-Equity Index"
    ) +
    theme_bw() + 
    scale_y_continuous(breaks = seq(0, 1, by = 0.25)) + 
    geom_signif(
      data = predictions_year,
      aes(x = year, y = emmean),
      comparisons = pairs,
      annotation = "",
      map_signif_level = TRUE,
      textsize = 7, 
      y_position = position, 
      col = "black"
    )  + 
    theme(
      # axis.text = element_text(size = 10), 
      axis.title = element_text(size = 14))
  
  ## Occurrence by agegroup
  formula_emm <- as.formula("pairwise ~ agegroup")
  
  predictions_agegroup <- emmeans(
    beta, 
    formula_emm, 
    adjust = "tukey", 
    type = "response", 
    weights = "equal"
  )$emmeans %>% 
    data.frame() %>% 
  mutate(
    emmean = (emmean*nrow(data) - 0.5)/(nrow(data)-1),
    asymp.LCL = (asymp.LCL*nrow(data) - 0.5)/(nrow(data)-1), 
    asymp.UCL = (asymp.UCL*nrow(data) - 0.5)/(nrow(data)-1),
    asymp.LCL = ifelse(asymp.LCL < 0, 0, asymp.LCL),
    asymp.UCL = ifelse(asymp.UCL > 1, 1, asymp.UCL))
  
  comparaisons_agegroup <- emmeans(
    beta, 
    formula_emm, 
    adjust = "tukey", 
    type = "response", 
    weights = "equal"
  )$contrasts %>%  
    data.frame() 
  
  pairwise_agegroup <- comparaisons_agegroup %>% 
    filter(p.value <= 0.05)
  
  pairwise_graph <- pairwise_agegroup |>  
    separate(contrast, c("var1", "var2"), extra = "merge")
  
  pairwise_graph$var1 <- gsub("agegroup", "", pairwise_graph$var1) %>% as.character()
  pairwise_graph$var2 <- gsub("agegroup", "", pairwise_graph$var2) %>% as.character()
  
  pairs_agegroup <- lapply(
    1:nrow(pairwise_graph), 
    function(i) list(c(pairwise_graph$var1[i], pairwise_graph$var2[i]))
  )
  
  pairs_agegroup <- unlist(pairs_agegroup, recursive = FALSE)
  
  position_agegroup <- seq(
    from = max(predictions_agegroup$asymp.UCL) + 0.05, 
    to = max(predictions_agegroup$asymp.UCL) + 0.05 + 0.05 * nrow(pairwise_graph), 
    by = 0.05
  )
  
  # Generate occurrence plot by agegroup
 agegroup_plot <- ggplot() +
    geom_jitter(
      data = data, 
      aes(x = agegroup, y = shannonEquity), 
      col = "grey", alpha = 0.8, 
      width = 0.2, height = 0
    ) +
    geom_errorbar(
      data = predictions_agegroup, 
      aes(x = agegroup, ymin = asymp.LCL, ymax = asymp.UCL), 
      width = 0.2
    ) + 
    geom_point(
      data = predictions_agegroup, 
      aes(x = agegroup, y = emmean), 
      size = 3
    ) + 
    labs(
      x = NULL, 
      y = "Shannon-Equity Index"
    ) +
    theme_bw() + 
    scale_y_continuous(breaks = seq(0, 1, by = 0.25)) + 
    geom_signif(
      data = predictions_agegroup,
      aes(x = agegroup, y = emmean),
      comparisons = pairs_agegroup,
      annotation = "",
      map_signif_level = TRUE,
      textsize = 7, 
      y_position = position_agegroup, 
      col = "black"
    )  + 
    theme(
      # axis.text = element_text(size = 10), 
      axis.title = element_text(size = 14))
  
  # Combine plots
  fig <- (year_plot) + (agegroup_plot + labs(y = NULL))
  
  # Combine significant pairwise comparisons
  signif <- rbind.fill(comparaisons, comparaisons_agegroup)
  
  # Residuals 
  residuals <- createDHARMa(
    simulatedResponse = as.matrix(
      simulate(beta, nsim = n_simulations)), 
    observedResponse = data$restricted_prop, 
    fittedPredictedResponse = predict(beta))

  # Return results as a list
  return(list(
    model_summary, 
    fig, 
    predictions_year,
    predictions_agegroup,
    signif,
    beta, 
    data, 
    residuals
  ))
}
```

```{r}
diversity_model <- diversitymodeling(diversity)

save(diversity_model, file = "../4_MANUSCRIPT/output/figures/diversity.Rda")
```

# Individual diet information used in the manuscript to generate heat-plot

```{r}
ww_modeling <- ww

save(ww_modeling, file = "../4_MANUSCRIPT/output/figures/ww.Rda")
```
